### 2018-07-11 Sections/quality_of_service.tex
minor

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a dephasing error model in this instance, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} = F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1,	
\end{align}
which corresponds to a bit-flip error model (Sec.~\ref{sec:dephasing_error}). That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.

@@

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} (see Sec.~\ref{sec:bell_proj} for an optical implementation) on their two qubits, whose measurement outcomes indicate whether two qubits were equal ($+$) or different ($-$). These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}. They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections. This is best illustrated by example.

\begin{figure}[!htb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}).}\label{fig:parity_meas}
\end{figure}

For this model, we will assume our parity projections destroy the first of their two input qubits, while the second one remains as the output. Then two such projections project a 4-qubit state down to a 2-qubit state as desired.

@@

@@

@@

The full circuit for this entanglement purification protocol is shown in Fig.~\ref{fig:ent_purif_circ}.

Similar reasoning as above can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.

In Sec.~\ref{sec:ent_purif} we demonstrate a simple linear optics setup for implementing this, that was subject to experimental demonstration.

>>>>

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
\end{align}
That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.

@@

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}. They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections.

\begin{figure}[!htb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}
\end{figure}

Two such parity projections project a 4-qubit state down to a 2-qubit state. The full circuit for this entanglement purification protocol is shown in Fig.~\ref{fig:ent_purif_circ}.

\subsubsection{Operation of protocol}

Let us illustrate the operation of the circuit by example of different possible input states.

\paragraph{No errors}

@@

\paragraph{One error}

@@

\paragraph{Two errors}

@@
